---
title: "MA_615_Final_Project_Yelp"
author: "Laura"
date: "12/16/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message=FALSE)
pacman::p_load(
yelpr,
readxl,
tidyverse,
magrittr,
gridExtra,
scales,
highcharter,
leaflet,
pander,
maps,
tidytext,
stringr,
wordcloud,
reshape2,
plotly
)

```

## Yelp Restaurant Rating and Review Analysis
*- Focus on Japanese restaurant in three main cities - New York, Dallas and San Fransisco.  
*- Data from Yelp API.


## Introduction

This project aimed to explore Japanese restaurants' ratings and reviews in there most popular cities in US. Which are New York, San Fransisco and Dallas.

- First we will explor the rating distributions of restaurant in different cities.

- Then we will dive in their geographical location distritutions to see the clustering on a geographical scale. (Pls refer to Shiny App)

- Finally we will explore on the review data to find the frequency of popular words in the reviews of    high-reviewing restaurants and also sentiments words clouds to see their positive and negative words distributions.


## Data Preparation

- Extrac Data via Yelp API
- Restaurant/Business Data
- Reveiw Data

key <- textreadr::read_rtf("API.rtf")  
  
Location: New York City, San Francisco, Dallas  
  
Categories : Restaurants  
  
Term: Japanese  
  
** Data reading please refer read_data.R file  

```{r,echo =FALSE }
new_york <- read.csv("./data/ny.csv",stringsAsFactors = FALSE)
sf <- read.csv("./data/sf.csv",stringsAsFactors = FALSE)
dallas <- read.csv("./data/dallas.csv",stringsAsFactors = FALSE)
business_all <- bind_rows(mutate(new_york, city = "NYC"),
          mutate(sf, city = "SF"),
          mutate(dallas, city = "Dallas"))
df_map <- business_all[-which(is.na(business_all$latitude)),]
```


## EDA
-Summary of the Restaurant Data and Average Review Ratings by City.

```{r,echo =FALSE }

dataGroupByCityStar <- business_all %>% 
    mutate(tsum = n()) %>% 
    group_by(city, rating) 

dataForTableByCityStar <- dataGroupByCityStar %>% group_by(city) %>%
    summarise(total_business = n(), total_reviews = sum(review_count), avg_rating = round(mean(rating),2)) %>%
                  arrange(desc(avg_rating))
library(pander)
panderOptions("digits", 3)
pander(dataForTableByCityStar, caption = "Japanese Food Restaurant")

```


## EDA
Ratings Score Distribution

```{r,echo =FALSE }

plot1 <-  ggplot(df_map,aes(x=rating)) + geom_bar(aes(color=city,fill=city),color = "white") +labs(y = "Counts",x="Rating",title="All Three Cities Ratings ")

plotly_build(plot1)


```


## EDA
Ratings Score Distribution By City  

```{r,echo =FALSE }

plot2 <- ggplot(df_map,aes(x=rating)) + geom_bar(aes(color=city,fill=city),color = "white") + facet_wrap(~factor(city))+labs(y = "Counts",x="Rating",title="Rating by City")

plotly_build(plot2)

```

## EDA
Ratings Score Distribution By Price Level  

```{r,echo =FALSE }

plot3 <- ggplot(df_map,aes(x=rating)) + geom_bar(aes(color=price,fill=city),color = "white") + facet_wrap(~factor(price))+labs(y = "Counts",x="Rating",title="Rating by Price")
plotly_build(plot3)
```

## EDA
We can see that most of the ratings are concenrated on 4 scores, Average Japanese restaurant ratings in New York is higher then the other two cities.


## Mapping
- smaller Blue--Rating <= 3.5
- Orange--Rating = 4
- Red--Rating >= 4.5
```{r,echo =FALSE}
getColor <- function(df_map) {
    sapply(df_map$rating, function(rating) {
        if(rating <=3.5) {
            "blue"
        } else if(rating <=4) {
            "orange"
        } else {
            "red"
        } })
}


icons <- awesomeIcons(
    icon = 'cutlery',
    iconColor = 'black',
    library = 'fa',
    markerColor = getColor(df_map),
    spin=T
)

mapStates = map("state", fill = TRUE, plot = FALSE)

leaflet() %>%    
    addProviderTiles(providers$CartoDB.Positron)%>%
    addPolygons(data = mapStates,fillColor = topo.colors(10, alpha = NULL), stroke = FALSE)%>% 
    addAwesomeMarkers(data = df_map, ~longitude, ~latitude, icon=icons,
                      label=~as.character(price),clusterOptions = T) 
```


## Text Mining
Frequent words in New York Japanese Restaurant
```{r,echo =FALSE}
ny_high_review_r <- read.csv("./data/ny_high_review.csv",stringsAsFactors = FALSE)
sf_high_review_r <- read.csv("./data/sf_high_review.csv",stringsAsFactors = FALSE)
dl_high_review_r <- read.csv("./data/dl_high_review.csv",stringsAsFactors = FALSE)


#### Prepare tidy test data 

### NY
tidy_ny <- ny_high_review_r %>% unnest_tokens(word, text)

tidy_ny <- tidy_ny %>%
    anti_join(stop_words)


# tidy_ny %>%
#     count(word, sort = TRUE) 

### SF
tidy_sf <- sf_high_review_r%>% unnest_tokens(word, text)

tidy_sf <- tidy_sf %>%
    anti_join(stop_words)


# tidy_sf %>%
#     count(word, sort = TRUE) 


### Dallas
tidy_dl <- dl_high_review_r %>% unnest_tokens(word, text)

tidy_dl <- tidy_dl %>%
    anti_join(stop_words)


# tidy_dl %>%
#     count(word, sort = TRUE) 

## Plot
tidy_ny %>%
    count(word, sort = TRUE) %>%
    filter(n > 50) %>%
    mutate(word = reorder(word, n)) %>%
    ggplot(aes(word, n)) +
    geom_col() +
    ggtitle("New York")+
    xlab(NULL) +
    coord_flip()



```

## Text Mining
Frequent words in San Fransisco Japanese Restaurant
```{r,echo =FALSE}
tidy_sf %>%
    count(word, sort = TRUE) %>%
    filter(n > 20) %>%
    mutate(word = reorder(word, n)) %>%
    ggplot(aes(word, n)) +
    geom_col() +
    ggtitle("San Fransisco")+
    xlab(NULL) +
    coord_flip()

```

## Text Mining
Frequent words in Dallas Japanese Restaurant
```{r,echo =FALSE}
tidy_dl %>%
    count(word, sort = TRUE) %>%
    filter(n > 20) %>%
    mutate(word = reorder(word, n)) %>%
    ggplot(aes(word, n)) +
    geom_col() +
    ggtitle("Dallas")+
    xlab(NULL) +
    coord_flip()
```



## Text Mining
```{r,echo =FALSE}
library(tidyr)

frequency <- bind_rows(mutate(tidy_ny, city = "NYC"),
                       mutate(tidy_sf, city = "SF"),
                       mutate(tidy_dl, city = "Dallas")) %>% 
    mutate(word = str_extract(word, "[a-z']+")) %>%
    count(city, word) %>%
    group_by(city) %>%
    mutate(proportion = n / sum(n)) %>% 
    select(-n) %>% 
    spread(city, proportion) %>% 
    gather(city, proportion, `NYC`:`SF`)


library(scales)

# expect a warning about rows with missing values being removed
ggplot(frequency, aes(x = proportion, y = `Dallas`, color = abs(`Dallas` - proportion))) +
    geom_abline(color = "gray40", lty = 2) +
    geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
    geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
    scale_x_log10(labels = percent_format()) +
    scale_y_log10(labels = percent_format()) +
    scale_color_gradient(limits = c(0, 0.001), low = "darkslategray4", high = "gray75") +
    facet_wrap(~city, ncol = 2) +
    theme(legend.position="none") +
    labs(y = "Dallas", x = NULL)

### Let’s quantify how similar and different these sets of word frequencies are using a correlation test. 
### How correlated are the review words frequencies between NYC and SF in high restaurant?
```


## Text Mining
- a
From Below two slides we can see that NYC and Dallas have more correlation in restaurant reciews in high ratings restaurant than with San Fransisco
```{r,echo =FALSE}
### How correlated are the review words frequencies between NYC and SF in high restaurant?

cor.test(data = frequency[frequency$city == "SF",],
         ~ proportion + `Dallas`)

```

## Text Mining
- b
```{r,echo =FALSE}
### How correlated are the review words frequencies between NYC and SF in high restaurant?

cor.test(data = frequency[frequency$city == "NYC",],
         ~ proportion + `Dallas`)
```

## Text Mining
- Word cloud 
- NYC Most frequent words in high-rating restaurant reviews
```{r}
library(wordcloud)
custom_stop_words <- bind_rows(tibble(word = c("food","restaurant"), 
                                      lexicon = c("custom")), 
                               stop_words)


tidy_ny %>%
    anti_join(custom_stop_words) %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))

```

## Text Mining
- Word cloud 
- SF Most frequent words in high-rating restaurant reviews
```{r}
library(wordcloud)
custom_stop_words <- bind_rows(tibble(word = c("food","restaurant"), 
                                      lexicon = c("custom")), 
                               stop_words)


tidy_sf %>%
    anti_join(custom_stop_words) %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))

```


## Text Mining
- Word cloud 
- Dallas Most frequent words in high-rating restaurant reviews
```{r}
library(wordcloud)
custom_stop_words <- bind_rows(tibble(word = c("food","restaurant"), 
                                      lexicon = c("custom")), 
                               stop_words)


tidy_dl %>%
    anti_join(custom_stop_words) %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))


```




